### Problem 1
```{r}
require(ISLR)
require(MASS)
require(pROC)
set.seed(3315)
```

```{r}
load("mnist_all.RData")
index.35.train <- train$y == 3 | train$y == 5
train.35 <- as.data.frame(train$x[index.35.train,])
train.35$z <- as.numeric(train$y[index.35.train] == 5)
index.35.test <- test$y == 3 | test$y == 5
test.35 <- as.data.frame(test$x[index.35.test,])
test.35$z <- as.numeric(test$y[index.35.test] == 5)
```

```{r}
train.var <- apply(train.35[,1:784],2,FUN = sd)
train.order = order(train.var, decreasing = T)
head(train.order, 10)
```
```{r}
model.25 <- glm(z ~ V403, data = train.35, family = binomial)
summary(model.25)
```
#Comment

Instead of using all the pixels, utilizing only the important pixels is meaningful to reduce computation complexity.
### Problem 2

#(a)
```{r}
library(ISLR)
data(Weekly)
head(Weekly)
```

```{r}
library(ggplot2)
ggplot(Weekly, aes(x=Lag1,y=Lag2,color=Direction))+
  geom_point()
ggplot(Weekly, aes(x=Lag2,y=Volume,color=Direction))+
  geom_point()
```
```{r}
library(dplyr)
down_week=filter(Weekly,Direction=='Down')
up_week=filter(Weekly,Direction=='Up')

t.test(down_week$Lag1,up_week$Lag1,'greater')
t.test(down_week$Lag2,up_week$Lag2,'less')
t.test(down_week$Lag3,up_week$Lag3,'two.sided')
t.test(down_week$Lag4,up_week$Lag4,'two.sided')
t.test(down_week$Lag5,up_week$Lag5,'two.sided')
t.test(down_week$Volume,up_week$Volume,'two.sided')
```

# Comment
From the scatter plot, we can see the points of different directions are highly overlapping. And from the t-test we can see there are evidences in the difference between Lag1 and Lag2 of different directions.

#(b)
```{r}
library(stats)
simple_weekly = Weekly[,c('Lag1','Lag2','Lag3','Lag4','Lag5','Volume')]
simple_weekly['Direction'] =ifelse(Weekly$Direction=='Up',1,0)
simple_weekly$Direction = as.factor(simple_weekly$Direction)

model1 <- glm(Direction~Lag1+Lag2+Lag3+Lag4+Lag5+Volume, data=simple_weekly, family='binomial')
summary(model1)
```

# Comment
Only Lag2 appears to be statistically significant.

#(c)
```{r}
library(caret)
pred <- as.factor(ifelse(predict(model1,type='link')>0,1,0))

confusionMatrix(pred,simple_weekly$Direction)
```

#Comment 
Many false positives emerge.

#(d)
```{r}
train=filter(Weekly, Year %in% seq(1990,2008))
test=filter(Weekly, Year %in% seq(2009,2010))

simple_train =  train[,c('Lag1','Lag2','Lag3','Lag4','Lag5','Volume')]
simple_train['Direction'] = ifelse(train$Direction=='Up',1,0)
simple_train$Direction = as.factor(simple_train$Direction)

simple_test =  test[,c('Lag1','Lag2','Lag3','Lag4','Lag5','Volume')]
simple_test['Direction'] = ifelse(test$Direction=='Up',1,0)
simple_test$Direction = as.factor(simple_test$Direction)



model2 <- glm(Direction~Lag2, data=simple_train, family='binomial')

pred2 <- as.factor(ifelse(predict(model2, simple_test)>0,1,0))

cm<-confusionMatrix(pred2,simple_test$Direction)
```

```{r}
cm$overall['Accuracy']
```
